Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-14 paper.tex
update graphs

\begin{figure}
    \label{fig:trans}
    % Transitivity with precompilation.
    % 
    \begin{tikzpicture}
        \begin{axis}[
            title={Transitivity rule},
            xlabel={Number of hypotheses},
            ylabel={Time in ms},
            xmin=2, xmax=6,
            ymin=2^3, ymax=2^13,
            xtick={2,3,4,5,6},
            ytick={2^3,2^5,2^7,2^9,2^11,2^13},
            ymode=log,
            %xmode=log,
            log basis y=2,
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
        ]

        \addplot[
            color=orange,
            mark=square,
            ]
            coordinates {
                (2, 74.566944) (3, 444.481222) (4, 811.149916) (5, 2955.663569) (6, 4703.832541) 
            };
            \addlegendentry{Stateless}
        \addplot[
            color=blue,
            mark=square,
            ]
            coordinates {
                (2, 13.089680) (3, 12.556333) (4, 14.278986) (5, 17.385902) (6, 20.682083)
            };
            \addlegendentry{Stateful}
        \end{axis}
        \end{tikzpicture}
    \end{figure}

@@

\begin{figure}
    %Indep with precompilation
        \begin{tikzpicture}
            \begin{axis}[
                title={Independance Test},
                xlabel={Number of Rules},
                ylabel={Time in ms},
                xmin=0, xmax=32,
                ymin=0, ymax=1700,
                ymode=log,xmode=log,
                log basis x=2,
                log basis y=2,
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
            ]

            \addplot[
                color=blue,
                mark=square,
                ]
                coordinates {
                (1, 0.710963)(2, 1.266787)(4, 2.181111)(8, 4.220279)(16, 8.084744)(32, 15.683840)
                };
                \addlegendentry{Stateful}
            \addplot[
                color=orange,
                mark=square,
                ]
                coordinates {
                (1, 0.872730)(2, 2.100940)(4, 7.245598)(8, 35.805959)(16, 222.283526)(32, 1600.978502)
                };
                \addlegendentry{Stateless}
            \end{axis}
            \end{tikzpicture}
        \end{figure}

@@

\begin{figure}
    \label{fig:erase}
%erase with precompilation
    \begin{tikzpicture}
        \begin{axis}[
            title={Depth Test},
            xlabel={Depth},
            ylabel={Time in ms},
            xmin=0, xmax=6,
            ymin=3, ymax=7,
            xtick={0,1,2,3,4,5,6},
            ytick={3,4,5,6,7},
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
        ]

        \addplot[
            color=blue,
            mark=square,
            ]
            coordinates {
            (1, 3.715813)(2, 3.893547)(3, 3.856956)(4, 3.722684)(5, 3.714804)(6, 3.900508)
            };
            \addlegendentry{Stateful}
        \addplot[
            color=orange,
            mark=square,
            ]
            coordinates {
            (1, 2.993757)(2, 3.585232)(3, 3.880661)(4, 4.098640)(5, 4.322570)(6, 5.765420)
            };
            \addlegendentry{Stateless}
        \end{axis}
        \end{tikzpicture}
    \end{figure}

>>>>

\begin{figure}
    \label{fig:trans}
    % Transitivity without precompilation.
    % 
    \begin{tikzpicture}
        \begin{axis}[
            title={Transitivity rule},
            xlabel={Number of hypotheses},
            ylabel={Time in ms},
            xmin=1, xmax=16,
            ymin=2^3, ymax=2^13,
            xtick={1,2,4,8,16},
            ytick={2^3,2^5,2^7,2^9,2^11,2^13},
            xmode=log,
            ymode=log,
            log basis x=2,
            log basis y=2,
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
            legend image post style={mark=},
        ]

        \addplot[
            color=orange,
            mark=square,
            ]
            coordinates {
              (1, 7.663472) (2, 9.354750) (4, 15.768194) (8, 104.921791) (16, 1882.683111)
            };
            \addlegendentry{Stateless}
        \addplot[
            color=blue,
            mark=square,
            ]
            coordinates {
              (1, 10.308541) (2, 10.704638) (4, 16.274305) (8, 38.800833) (16, 179.697681) 
            };
            \addlegendentry{Stateful}
            \addplot[
              color=orange,
              mark=o,
              ]
              coordinates {
                (1, 10.591138) (2, 23.881333) (4, 142.013389) (8, 1676.148375) (16, 24327.359417)
              };
          \addplot[
              color=blue,
              mark=o,
              ]
              coordinates {
                (1, 13.974694) (2, 26.216833) (4, 68.953444) (8, 245.601028) (16, 1028.670680) 
              };
        \end{axis}
        \end{tikzpicture}
    \end{figure}

@@

\begin{figure}
    %Indep without precompilation
        \begin{tikzpicture}
            \begin{axis}[
                title={Independance Test},
                xlabel={Number of Rules},
                ylabel={Time in ms},
                xmin=1, xmax=32,
                ymin=2^3, ymax=1700,
                ymode=log,xmode=log,
                log basis x=2,
                log basis y=2,
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                legend image post style={mark=},
            ]

            \addplot[
              color=orange,
              mark=square,
              ]
              coordinates {
                (1, 10.399958) (2, 16.426541) (4, 43.461403) (8, 205.595541) (16, 1238.090889) (32, 8927.857819) 
              };
              \addlegendentry{Stateless}
            \addplot[
                color=blue,
                mark=square,
                ]
                coordinates {
                  (1, 11.231875) (2, 12.879500) (4, 16.851930) (8, 24.666485) (16, 42.054055) (32, 76.369778) 
                };
                \addlegendentry{Stateful}
                \addplot[
              color=orange,
              mark=o,
              ]
              coordinates {
                (1, 19.405222) (2, 33.487472) (4, 80.107597) (8, 284.954791) (16, 1536.089624) (32, 10721.729861)
              };
            \addplot[
                color=blue,
                mark=o,
                ]
                coordinates {
                  (1, 25.892069) (2, 40.031930) (4, 69.446902) (8, 130.640986) (16, 260.653917) (32, 481.827902)
                };
            \end{axis}
            \end{tikzpicture}
        \end{figure}

@@

\begin{figure}
    \label{fig:erase}
%erase without precompilation
    \begin{tikzpicture}
        \begin{axis}[
            title={Depth Test},
            xlabel={Depth},
            ylabel={Time in ms},
            xmin=1, xmax=6,
            ymin=6, ymax=20,
            xtick={1,2,3,4,5,6},
            ytick={10,15},
            legend pos=north west,
            ymajorgrids=true,
            grid style=dashed,
            legend image post style={mark=},
        ]
        \addplot[
            color=orange,
            mark=square,
            ]
            coordinates {
              (1, 6.407973) (2, 9.831676) (3, 10.301718) (4, 10.626144) (5, 11.261754) (6, 11.795240) 
            };
            \addlegendentry{Stateless}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 15.835558) (2, 16.961994) (3, 16.424259) (4, 17.605449) (5, 15.691536) (6, 14.982820) 
          };
          \addlegendentry{Stateful}
        \end{axis}
        \end{tikzpicture}
    \end{figure}
